Versioned data: why it is needed and how it can be achieved (easily and cheaply)

### 2017-09-25 ms.tex
added acknowledgements section. please add yours.

\title{Versioned data: why it is needed and how it can be achieved (easily and cheaply)}
\author{Daniel S. Falster$^1$, Richard G. FitzJohn$^2$,\\ Matthew
  W. Pennell$^3$, and William K. Cornwell$^{1,*}$}
\affiliation{
$^1$ Evolution \& Ecology Research Centre, School of Biological, Earth and Environmental Sciences,\\
$^2$ School of Public Health, Imperial College, London SW7 2AZ United Kingdom\\
University of New South Wales, Sydney, NSW 2052, Australia\\
$^3$ Department of Zoology and Biodiversity Research Centre,\\
University of British Columbia, Vancouver, B.C. V6T 1Z4 Canada\\
$^*$ Corresponding author: w.cornwell@unsw.edu.au\\
}
\date{}

@@

>>>>

\title{Versioned data: why it is needed and how it can be achieved (easily and cheaply)}
\author{Daniel S. Falster$^1,*$, Richard G. FitzJohn$^2$,\\ Matthew
  W. Pennell$^3$, and William K. Cornwell$^{1,*}$}
\affiliation{
$^1$ Evolution \& Ecology Research Centre, School of Biological, Earth and Environmental Sciences,\\
$^2$ School of Public Health, Imperial College, London SW7 2AZ United Kingdom\\
University of New South Wales, Sydney, NSW 2052, Australia\\
$^2$ Imperial College, London, United Kingdom\\
$^3$ Department of Zoology and Biodiversity Research Centre,\\
University of British Columbia, Vancouver, B.C. V6T 1Z4 Canada\\
$^*$ Corresponding author: daniel.falster@unsw.edu.au\\
}
\date{}

@@

\section{Acknowledgements}

M.W.P. was funded by a NSERC Discovery Grant.
